Paper Analysis

### 2025-04-25 Paper_WriteUp/Paper_Plots.qmd
update fig3 height
fixing model path and using better way to remove duplicate rows

ggsave(plot = comp_global,
       filename = paste0(here("Paper_WriteUp", "paper_figures", "fig3.png")), dpi = 600,
       height = 5, width = 7)
```

@@

#read in the model and users
model = readRDS(file = here(model_path, "all_rated_bullet_model_prev_n1.RDS"))
users = readRDS(file = here(model_path, "users_bullet.RDS"))

@@

#selecting bullet 60+0 only
bullet_60 = lichess_data  %>%
  mutate(Event = tolower(Event)) %>%
  filter(Event == "rated bullet game", Variant == "Standard", TimeControl == "60+0") %>%
  dplyr::select(c("White", "Black", "Result", "UTCDate", "UTCTime", "Username", "WhiteElo", "BlackElo"))

#remove the duplicate rows
bullet_60_no_dup = bullet_60[!duplicated(bullet_60),]

#final 1000 games each user plays
last_games = bullet_60_no_dup %>%
  filter(Username %in% users) %>%  
  group_by(Username) %>%
  arrange(UTCDate, UTCTime, .by_group = TRUE) %>%
  slice_tail(n = 1000) %>%
  ungroup()

@@

#true glicko rating of all games before last 1000
true_glicko_first = bullet_60_no_dup |> 
  filter(Username == users[focal_player_used]) |> 
  arrange(UTCDate, UTCTime) |> 
  slice(1:(n() - 1000)) |> 
  mutate(game = row_number(), glicko = ifelse(Username == White, WhiteElo, BlackElo)) %>%
  dplyr::select(game, glicko)
num_prev = nrow(true_glicko_first) #number of games before final simulated games

>>>>

ggsave(plot = comp_global,
       filename = paste0(here("Paper_WriteUp", "paper_figures", "fig3.png")), dpi = 600,
       height = 3.5, width = 7)
```

@@

#read in the model and users
model = readRDS(file = here(model_path, "mid_fit.RDS"))
users = readRDS(file = here(model_path, "users_bullet.RDS"))

@@

#selecting bullet 60+0 only
bullet_60 = lichess_data  %>%
  mutate(Event = tolower(Event)) %>%
  filter(Event == "rated bullet game", Variant == "Standard", TimeControl == "60+0") %>%
  dplyr::select(c("White", "Black", "Result", "UTCDate", "UTCTime", "Username", "WhiteElo", "BlackElo")) %>%
  distinct() #remove the duplicate rows if they exist

#final 1000 games each user plays
last_games = bullet_60 %>%
  filter(Username %in% users) %>%  
  group_by(Username) %>%
  arrange(UTCDate, UTCTime, .by_group = TRUE) %>%
  slice_tail(n = 1000) %>%
  ungroup()

@@

#true glicko rating of all games before last 1000
true_glicko_first = bullet_60 |> 
  filter(Username == users[focal_player_used]) |> 
  arrange(UTCDate, UTCTime) |> 
  slice(1:(n() - 1000)) |> 
  mutate(game = row_number(), glicko = ifelse(Username == White, WhiteElo, BlackElo)) %>%
  dplyr::select(game, glicko)
num_prev = nrow(true_glicko_first) #number of games before final simulated games
